---
title: "Cumulative Economically Significant Final Rules by Administration in first year"
author: "Yaxin Zhuang"
date: "`r Sys.Date()`"
output: html_document
---

## Initialize

We begin by initializing the Rmarkdown file. This is where we set relevant parameters and establish where this markdown file is located within the project directory, using the `[here](https://here.r-lib.org/reference/i_am.html)` package.

The `i_am` function indicates that `workflow_demo.Rmd` is located within the `code` folder inside the main project directory. In other words, the project root is located immediately above the `code` folder. All future calls to files are based on their relative location to the project root.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set location of this file in project directory
here::i_am("code/Cumulative Economically Significant Final Rules by Administration in first year.Rmd")
```

Import the packages required for the remainder of the rmarkdown file. It's easier to keep track of the necessary packages when all imports occur at the top of the file.

## Load Packages

```{r imports, results='hide', warning=FALSE}

# load packages
library(ggplot2)
library(showtext)
library(png)
library(ggpattern)
library(tidyr)
library(ggrepel)
library(dplyr)
library(scales)
library(gcookbook)


```

## Load Style

```{r load style}
# load style
source(here("code", "style.R"))
```

## Load data



```{r load_data}

# load csv using here
cun_sig_first <- read.csv(here("data","Cumulative_ES_rules_published_months_in_office_071023.csv"))

# eventually separate this into another file for reuse, then import/call the function
get_png <- function(filename) {
  grid::rasterGrob(png::readPNG(filename),interpolate = TRUE) # adjust logo size dimensions here
}

l <- get_png(here("code", "RSC_logo.png"))

#load custom font
font_add("avenir_lt_pro","a-avenir-next-lt-pro.otf")
showtext_auto()

```


## Process data


```{r clean_data}

cun_sig_first <- cun_sig_first[c(2:13), ]


# rename columns (will need to manually update with the names of new presidents)
colnames(cun_sig_first) <- c("month", "months_in_office", "Reagan", "Bush_41", "Clinton", "Bush_43", "Obama", "Trump", "Biden")

# get rid of unnecessary columns (will also need to manually update with new president names here)
cun_sig_first <- cun_sig_first[ , c("months_in_office", "Reagan", "Bush_41", "Clinton", "Bush_43", "Obama", "Trump", "Biden")]


# create long data frame (will also need to manually add new president's names here)
cun_sig_first_NA <- pivot_longer(cun_sig_first, cols = c("Reagan", "Bush_41", "Clinton", "Bush_43", "Obama", "Trump", "Biden"), names_to = "president", values_to = "econ_rules")

# convert to num to find and remove null
cun_sig_first_NA$months_in_office<- as.numeric(cun_sig_first_NA$months_in_office)
cun_sig_first_NA$econ_rules <- as.numeric(cun_sig_first_NA$econ_rules)

# remove NA values from long data frame (these NA values are the potential econ_rules values for presidents who didn't/haven't yet served the maximum number of months)
cun_sig_first_long <- cun_sig_first_NA[complete.cases(cun_sig_first_NA), ] # data frame need clean



```


## Plot data


```{r plot_data, results='markup'}


# change president column to factor (assign levels and labels)
cun_sig_first_long <- cun_sig_first_long %>%
  mutate(president = factor(president,
                        levels = c("Reagan",
                                   "Bush_41",
                                   "Clinton",
                                   "Bush_43",
                                   "Obama",
                                   "Trump",
                                   "Biden"),
                        labels = c("Reagan",
                                   "Bush 41",
                                   "Clinton",
                                   "Bush 43",
                                   "Obama",
                                   "Trump",
                                   "Biden")))

# calculate the end points of the lines
line_ends <- cun_sig_first_long %>%
  group_by(president) %>%
  summarise(months_in_office_end = max(months_in_office), econ_rules_end = max(econ_rules))

#annotation
current_date <- format(Sys.Date(), "%B %d, %Y")
caption_text <- paste("Sources: Office of the Federal Register (federalregister.gov) for Biden administration and all subsequent administrations;\n       Office of Information and Regulatory Affairs (OIRA) (reginfo.gov) for all prior administrations.\n\nUpdated:", current_date)
wrapped_caption <- paste(strwrap(caption_text, width = 95), collapse = "\n")

# generate line graph
line1 <- ggplot(cun_sig_first_long, aes(x = months_in_office, y = econ_rules, color = president, group = president)) +
  geom_line(linewidth = 0.75) +
  geom_label_repel(data = line_ends,
                  aes(x = months_in_office_end, y = econ_rules_end, label = president),
                  nudge_x = 0, nudge_y = 10,
                  segment.size = 0.2,
                  size = 3,
                  point.size = 1,
                  box.padding = 0,
                  point.padding = 0,
                  min.segment.length = 0.9,
                  force = 3,
                  label.size = NA,
                  label.padding = 0,
                  label.r = 0,
                  fill = alpha(c("white"), 0.8)) +
  scale_color_manual(values = c("#C9102F",
                                "#008364",
                                "#033C5A",
                                "#AA9868",
                                "#0190DB",
                                "#FFC72C",
                                "#78BE20")) +
  annotation_custom(l, xmin = -5, xmax = 10, ymin = -10, ymax = -35) + # for logo (need to play around with these settings)
  coord_cartesian(clip = "off") +
  linetheme +
  xlab("Number of Months In Office") +
  ylab("Number of Economically Significant Rules Published") +
  ggtitle("Cumulative Economically Significant Final Rules \nby Administration in First Year") +
  labs(color = "President", caption = wrapped_caption) +
  scale_y_continuous(breaks = seq(0, max(cun_sig_first_long$econ_rules) + 25, by = 25),
                     expand = c(0, 0),
                     limits = c(-2, max(cun_sig_first_long$econ_rules) + 25)) +
  scale_x_continuous(breaks = seq(0, max(cun_sig_first_long$months_in_office), by = 4),
                     expand = c(0, 0),
                     limits = c(0, max(cun_sig_first_long$months_in_office)))

line1

# save line1 as pdf
#ggsave("Cumulative Economically Significant Final Rules by Administration in First.pdf", plot = line1, width = 12, height = 9, dpi = 300)

```
