---
title: "Agency Econonmically Significant Final Rules by Presidential Year"
author: "Deven Patel"
date: "2024-02-01"
output: html_document
---

## Initialize

The `i_am` function identifies where the Rmd is located within the main project directory. All future calls to files are based on their relative location to the project root.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set location of this file in project directory
library(here)
i_am("charts/code/agency_econ_significant_rules_by_presidential_year.Rmd")

# import local functions
source(here("charts", "code", "local_utils.R"))
source(here("charts", "code", "style.R"))

copy_all_data(here("data", "es_rules", "by_agency"), here("charts", "data"))

```

## Load packages

```{r load packages, results='hide', warning=FALSE}
library(ggpattern)
```

## Universal values and functions

```{r code}
# current date
current_date <- format(Sys.Date(), "%B %d, %Y")

# set caption text
caption_text <- paste("Sources: Office of the Federal Register (federalregister.gov) for
the years 2021 and onwards;\n Office of Information and Regulatory
Affairs (reginfo.gov) for all the prior years.\n\nUpdated:", current_date)

# set wrapped caption width
wrapped_caption <- paste(strwrap(caption_text, width = 65), collapse = "\n")

# define agencies, intervals, and titles
agencies = c("dhs", "doe", "doi", "dol", "dot", "ed", "epa", "hhs", "hud", "sba", "usda")
intervals = c(1,1,1,1,1,1,2,5,1,5,2)
chart_ref <- as.data.frame(list(agency = agencies, interval = intervals)) %>% 
  mutate(title = paste0("Economically Significant Final Rules Published by ", 
                  toupper(agency),
                  " Each Presidential Year"))

# data cleaning

clean <- function(data_0){
  colnames(data_0) <- c("year", "party", "rules")
  data_0$party <- as.factor(data_0$party)
  data_0$year <- as.numeric(data_0$year)
  return(data_0)
}

# charting function
col_number <- 3

graph <- function(dataset, interval, title){
  upper <- ydynam(dataset, interval, col_number)
  bar1 <- ggplot(dataset, aes(x = year, y = rules, fill = party, pattern = party)) +
  geom_bar_pattern(stat = "identity", width = 0.5,
                   position = position_dodge(preserve = "single"),
                   pattern_color = NA,
                   pattern_fill = lightblue, pattern_angle = 45,
                   pattern_density = 0.1, pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6) +
  scale_fill_manual(values = c(GWblue, red)) +
  scale_pattern_manual(values = c(Democratic = "stripe", Republican = "none")) +
  ggtitle(title) +
  ylab("Number of Rules") +
  xlab("") +
  scale_y_continuous(breaks = seq(0, upper, by = interval), 
                     expand = c(0, 0.0), 
                     limits = c(-2, upper)) +
  scale_x_continuous(breaks = seq(min(dataset$year),
                                  max(dataset$year))
                     ) +
  labs(caption = wrapped_caption) +
  theme(plot.caption = element_text(hjust = 1, margin = margin(t = 0, l = 36, b = 50, unit = "pt"))) +
  theme_RSC +
  coord_cartesian(ylim = c(0, upper),
                  xlim = c(min(dataset$year)-0.5,
                                max(dataset$year)+0.5),
                  expand = FALSE) +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 20, unit = "pt")),
    axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1),
    axis.ticks.x = element_blank(),
    axis.line.x = element_line(linewidth = 1, color = RSCgray),
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = RSCgray, linetype = "solid"),
    panel.grid.minor = element_blank()
  )
  
  bar1
  
  bar2 <- ggdraw() + 
  draw_plot(bar1) + 
  draw_image(logo, x = 0.1, y = 0.08, halign = 0, valign = 0, width = 0.2)
  
  bar2 
  return(bar2)
}


```

# all inclusive loop for data import, cleaning, charting, and saving
```{r}

out = here("charts", "output", "by_agency")
if (!dir.exists(out)){
  dir.create(out, showWarnings = FALSE)
  }

chart_n_save <- function(agency){
  data_file = paste0(agency, "_econ_significant_rules_by_presidential_year.csv")
  rules <- read.csv(here("charts", "data", data_file))
  rules1 <- clean(rules)
  interval <- chart_ref[which(chart_ref$agency==agency), 2]
  title <- chart_ref[which(chart_ref$agency==agency), 3]
  bar <- graph(rules1, interval, title)
  print(bar)
  ggsave(
    here("charts", "output", "by_agency", 
         paste0(agency, "_econ_significant_rules_by_presidential_year.pdf")
         ), 
    plot = get("bar"), 
    width = 12, 
    height = 9, 
    dpi = 300
    )
  ggsave(
    here("charts", "output", "by_agency", 
         paste0(agency, "_econ_significant_rules_by_presidential_year.png")
         ), 
    device = "png", 
    plot = get("bar"), 
    width = 1200, 
    height = 900, 
    units = "px", 
    dpi = 96, 
    bg = "white"
    )
  }

for (agency in agencies) {
  chart_n_save(agency)
 }

```

# Outputting individual charts as needed
```{r}
# define agency
agency <- "hhs"

# run each step of the loop
data_file = paste0(agency, "_econ_significant_rules_by_presidential_year.csv")
rules <- read.csv(here("charts", "data", data_file))
rules1 <- clean(rules)

# Interval can be replaced with any number
interval <- chart_ref[which(chart_ref$agency==agency), 2]
title <- chart_ref[which(chart_ref$agency==agency), 3]
bar <- graph(rules1, interval, title)
print(bar)

```
# Save individual charts as needed
```{r}
ggsave(
  here("charts", "output", "by_agency", 
       paste0(agency, "_econ_significant_rules_by_presidential_year.pdf")
       ), 
  plot = get("bar"), 
  width = 12, 
  height = 9, 
  dpi = 300
  )
ggsave(
  here("charts", "output", "by_agency", 
       paste0(agency, "_econ_significant_rules_by_presidential_year.png")
       ), 
  device = "png", 
  plot = get("bar"), 
  width = 1200, 
  height = 900, 
  units = "px", 
  dpi = 96, 
  bg = "white"
  )
```



