---
title: "Total_Pages_in_the_Code_of_Federal_Regulations"
author: "Yaxin Zhuang"
date: "`r Sys.Date()`"
output: html_document
---

## Initialize

We begin by initializing the Rmarkdown file. This is where we set relevant parameters and establish where this markdown file is located within the project directory, using the `[here](https://here.r-lib.org/reference/i_am.html)` package.

The `i_am` function indicates that `workflow_demo.Rmd` is located within the `code` folder inside the main project directory. In other words, the project root is located immediately above the `code` folder. All future calls to files are based on their relative location to the project root.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set location of this file in project directory
library(here)
i_am("charts/code/Total Pages Published in the Code of Federal Regulations.Rmd")

# import local functions
source(here("charts", "code", "local_utils.R"))
source(here("charts", "code", "style.R"))

# point to dataset
data_file = "cfr_pages_by_calendar_year.csv"

# refresh dataset
copy_dataset(data_file, here("data"), here("charts", "data"))

```

Import the packages required for the remainder of the rmarkdown file. It's easier to keep track of the necessary packages when all imports occur at the top of the file.

## Load Packages

```{r imports, results='hide', warning=FALSE}

# load packages
library(ggplot2)
library(showtext)
library(png)
library(ggpattern)
library(tidyr)
library(ggrepel)
library(dplyr)
library(scales)
library(gcookbook)
```

## Load Style

```{r load style}
# load style
source(here("code", "style.R"))
```

## Load data


```{r load_data}

# load csv using here
df <- read.csv("/content/TotalPagesCodeFedReg_11012022.csv")

# eventually separate this into another file for reuse, then import/call the function
get_png <- function(filename) {
  grid::rasterGrob(png::readPNG(filename),interpolate = TRUE) # adjust logo size dimensions here
}

l <- get_png(here("code", "RSC_logo.png"))

#load custom font
font_add("avenir_lt_pro","a-avenir-next-lt-pro.otf")
showtext_auto()

```

## Process data


```{r clean_data}

df1_1 <- df1[c(3:48),c(0:5)]

df1 <- df[c(16:87),c(0:3)]
colnames(df1) <- c("year", "color", "tolpages")

current_date <- format(Sys.Date(), "%B %d, %Y")
caption_text <- paste("Sources: Office of the Federal Register (federalregister.gov) for the years starting 2021;\n       Office of Information and Regulatory Affairs (OIRA) (reginfo.gov) for all prior years.\n\nUpdated:", current_date)

df2 = subset(df1, select = -c(color) )

df2$tolpages <- as.numeric(gsub(",","",df2$tolpages))

```


## Plot data


```{r plot_data, results='markup'}
# create caption text
caption_text <- paste("Sources:  Federal Register Statistics \n\nUpdated:", current_date)

# format wrapping setting for caption text
wrapped_caption <- paste(strwrap(caption_text, width = 95), collapse = "\n")


bar2 <-
  ggplot(data=df2, aes(x=year, y=tolpages)) +
  geom_bar(stat="identity", fill="#033C5A")+
  #geom_text(aes(label=len), vjust=-0.3, size=3.5)+

  ggtitle("Total Pages Published in the Code of Federal Regulations \n(1950-2021)") +
  ylab("Number of Pages") +
  xlab("") +
  scale_y_continuous(breaks = seq(0, max(df2$tolpages)+20000, by = 20000), expand = c(0, 0),
                     limits = c(-2, max(df2$tolpages)+20000),
                     labels = function(x) ifelse(x == 0, "0", scales::label_number(suffix = "k", scale = 1e-3)(x)),) +

  scale_x_discrete(breaks = seq(min(df2$year), max(df2$year), by = 2)) + # only display even year
  annotation_custom(l, xmin = -5, xmax = 20, ymin = 30000, ymax = -107000) + # for logo
  coord_cartesian(clip = "off") +
  mytheme+
  labs(caption = wrapped_caption)


bar3
#ggsave("Total Pages Published in the Code of Federal Regulations.pdf", plot = bar3, width = 12, height = 9, dpi = 300)

```